---
title: "p8105_hw1new_yl4358"
author: "YI LIU"
date: "9/20/2019"
output: github_document
---

# Problem 1

Here we create a data frame as instructed in the problem 1.

```{r pb1_create_df}

library(tidyverse)

first_df = tibble(
  sample = rnorm(8),
  vec_log = sample > 0,
  vec_char = c("My", "name", "is", "YI", "LIU", "and", "study", "biostatistics"),
  vec_factor = factor(c("high", "medium", "low", "high", "medium", "low", "low", "low"))
)
```

* The mean of the sample is `r mean(pull(first_df, sample))`.

* The mean of vec_log is `r mean(pull(first_df, vec_log))`.

* We can't take the mean of character vector and factor vector.



Here we convert variables from one type to another.

```{r pb1_convert_var_type, eval=FALSE}

as.numeric(pull(first_df, vec_log)) * pull(first_df, sample)
as.factor(pull(first_df, vec_log)) * pull(first_df, sample)
as.numeric(as.factor(pull(first_df, vec_log))) * pull(first_df, sample)

```

* We find that factor vector cannot do operation while the numeric can. This explain that we cannot take the mean of character vector and factor vector.


# Problem 2

Here we create a data frame as instructed in the problem 2.

```{r pb2_create_df}

second_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_log2 = (x + y) > 1,
  vec_num = as.numeric(vec_log2),
  vec_factor = as.factor(vec_log2)
)

```

* The dataset has `r nrow(second_df)` rows and `r ncol(second_df)` columns.

* The mean, median and standard deviation of x is `r mean(pull(second_df, x))`, `r median(pull(second_df, x))` and `r sd(pull(second_df, x))`.

* The proportion of cases for which x + y > 1 is `r sum(pull(second_df, vec_num))/length(pull(second_df, vec_num))`.


Here we make scatterplots!

```{r pb2_scatterplots}

ggplot(second_df, aes(x = x, y = y, color = "y vs x")) + geom_point()
ggsave("hw1new_plot1_yl4358.pdf")
ggplot(second_df, aes(x = x, y = vec_num, color = "vec_num vs x")) + geom_point()
ggplot(second_df, aes(x = x, y = vec_factor, color = "vec_factor vs x")) + geom_point()

```

